---
title: "204 Homework 4"
author: "Claire Powers and Tom Paschos"
date: "5/30/2018"
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages_data, include=FALSE}
library(tidyverse)
library(cowplot)
library(nlstools)
library(stats)
library(reshape2)
library(stats)

df <- read.csv("HW4Data.csv")
```
##Initial plots and exploring the data

- Red lines are linear models, blue lines are "loess" which basically just follows the data points
```{r Initial_plots, echo=FALSE}
a <- ggplot(df, aes(x=df$Abatement))+
  geom_smooth(method="loess",aes(y=df$MC_A))+
  geom_smooth(method="lm",se=F,color="red",aes(y=df$MC_A))+
  geom_point(aes(y=df$MC_A))+
  #ylim(-15,150)+
  ggtitle("A")+
  xlab("Tons of Carbon Emitted")+
  ylab("Marginal Cost\nof Abatement ($)")+
  theme_classic()
a

b <- ggplot(df, aes(x=df$Abatement))+
  geom_smooth(method="loess",aes(y=df$MC_B))+
  geom_smooth(method="lm",se=F,color="red",aes(y=df$MC_B))+
  geom_point(aes(y=df$MC_B))+
  #ylim(-15,150)+
  ggtitle("B")+
  xlab("Tons of Carbon Emitted")+
  ylab("Marginal Cost\nof Abatement ($)")+
  theme_classic()
b

c <- ggplot(df, aes(x=df$Abatement))+
  geom_smooth(method="loess",aes(y=df$MC_C))+
  geom_smooth(method="lm",se=F,color="red",aes(y=df$MC_C))+
  geom_point(aes(y=df$MC_C))+
  ggtitle("C")+
  xlab("Tons of Carbon Emitted")+
  ylab("Marginal Cost\nof Abatement ($)")+
  #ylim(-15,150)+
  theme_classic()
c

d <- ggplot(df, aes(x=df$Abatement))+
  geom_smooth(method="loess",se=F,aes(y=df$MC_D))+
  geom_smooth(method="lm",se=F,color="red",aes(y=df$MC_D))+
  geom_point(aes(y=df$MC_D))+
  ggtitle("D")+
  xlab("Tons of Carbon Emitted")+
  ylab("Marginal Cost\nof Abatement ($)")+
  #ylim(-15,150)+
  theme_classic()
d
plot_grid(a,b,c,d)
```

- Sector A: Linear

- Sector B: Logistic

- Sector C: Exponential

- Sector D: Linear segments

####Combining all data point for sectors A,B, and C. Potentially used for aggregate?
```{r combined_plot}
e <- ggplot(df, aes(x=df$Abatement))+
  geom_smooth(method="lm",aes(y=df$MC_A), se=FALSE)+
  geom_point(aes(y=df$MC_A))+
  geom_smooth(method="lm",aes(y=df$MC_B),se=FALSE)+
  geom_point(aes(y=df$MC_B),shape=4)+
  geom_smooth(method="lm",aes(y=df$MC_C),se=FALSE)+
  geom_point(aes(y=df$MC_C),shape=2)+
  geom_smooth(method="lm",aes(y=df$MC_D),se=FALSE)+
  geom_point(aes(y=df$MC_D),shape=3)+
  xlab("Tons of Carbon Emitted")+
  ylab("Marginal Cost\nof Abatement ($)")+
  ylim(-15,150)+
  theme_classic()
e

#Dataframe
df1 <- df %>% 
  select("Abatement","MC_A","MC_B","MC_C")
combo_df <- melt(df1, id=c("Abatement"))

combo_plot <- ggplot(combo_df, aes(x=Abatement))+
  geom_smooth(method="loess",aes(y=value))+
  geom_point(aes(y=value, color = variable, shape = variable))+
  xlab("Tons of Carbon Emitted")+
  ylab("Marginal Cost\nof Abatement ($)")+
  ylim(-15,150)+
  theme_classic()
combo_plot

combo_model <- lm(value~Abatement, data=combo_df)
summary(combo_model)
```
##Inidividual models for each sector
###Sector A.
```{r sector_A}
#Linear model
model_A <- lm(MC_A ~ Abatement, data=df)
summary(model_A)

plot(model_A)
AIC(model_A)

#Vector to use to make predictions
A_vector <- data.frame(seq(0,180,length.out=181))
colnames(A_vector) <- c("Abatement")

#Predictions
sector_A <- predict(model_A, newdata = A_vector,se.fit=TRUE,df=FALSE)

#Data.frame
A_df <- data.frame(A_vector,sector_A)
colnames(A_df) <- c("Abatement","MC_A","SE","DF","residuals")
  
#For 
#funA <- function(Abatement){
#  costA <- model_A$coefficients[1] + model_A$coefficients[2]*Abatement
#}
#sector_A$MC_A2 <- funA(sector_A$Abatement)

ggplot(A_df, aes(x=Abatement, y=MC_A))+
  geom_line()+
  geom_point(data=df, aes(x=Abatement, y=MC_A))+
  geom_segment(x=0,y=95,xend=180,yend=0)
```


##Sector B. 
```{r}
b
```

Integrated logistic Growth Equation
$$Cost(Abatement) = \frac{Max~Value}{(1+B*e^{rt})}$$
Initial estimates for values in the equation based on plot

-Max = 40

-C0 = 12

-B = (40-12)/12 ~ 2.33333

```{r r_est_and_NLS}
r_est <- lm(log(df$MC_B[1:5])~df$Abatement[1:5])
r_est

#Logistic equations using NLS
B_model <- nls(MC_B ~ maxValue/(1 + B*exp(-r*Abatement)),
                data = df,
                start = list(maxValue = 40, B = 2.33333, r = 0.006224),
                trace = TRUE)
summary(B_abatement_fit)

maxValue <- coef(B_abatement_fit)[1]
B <- coef(B_abatement_fit)[2]
r <- coef(B_abatement_fit)[3]

B_vector <- seq(0, 200, length = 200)
B_predict <- data.frame(predict(B_model, list(Abatement = B_vector), se.fit=TRUE))

B_df <- data.frame(B_vector, B_predict)
colnames(B_df) <- c("Abatement","MC_B")

ggplot(df, aes(x=Abatement, y=MC_B))+
  geom_point(color="blue", size = 3)+
  geom_smooth(data=B_df,aes(x=Abatement,y=))

B_model_lm <- lm(MC_B ~ Abatement, data=df)

plot(B_model_lm)
plot(B_model)

AIC(B_model_lm)
AIC(B_model)
```

