---
title: "3_EconHW4"
author: "Claire Powers"
date: "May 31, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r packages_data, include=FALSE}
library(tidyverse)
library(cowplot)
library(nlstools)
library(stats)
library(reshape2)
library(stats)

df <- read.csv("HW4Data.csv")
```

###Initial plots and exploring the data

- Red lines are linear models, blue lines are "loess" which basically just follows the data points
```{r Initial_plots, echo=FALSE}
a <- ggplot(df, aes(x=df$Abatement))+
  geom_smooth(method="lm",se=F,color="red",aes(y=df$MC_A))+
  geom_point(aes(y=df$MC_A))+
  #ylim(-15,150)+
  ggtitle("A")+
  xlab("Tons of Carbon Emitted")+
  ylab("Marginal Cost\nof Abatement ($)")+
  theme_classic()

b <- ggplot(df, aes(x=df$Abatement))+
  geom_smooth(method="lm",se=F,color="red",aes(y=df$MC_B))+
  geom_point(aes(y=df$MC_B))+
  #ylim(-15,150)+
  ggtitle("B")+
  xlab("Tons of Carbon Emitted")+
  ylab("Marginal Cost\nof Abatement ($)")+
  theme_classic()

c <- ggplot(df, aes(x=df$Abatement))+
  geom_smooth(method="lm",se=F,color="red",aes(y=df$MC_C))+
  geom_point(aes(y=df$MC_C))+
  ggtitle("C")+
  xlab("Tons of Carbon Emitted")+
  ylab("Marginal Cost\nof Abatement ($)")+
  #ylim(-15,150)+
  theme_classic()

d <- ggplot(df, aes(x=df$Abatement))+
  geom_smooth(method="lm",se=F,color="red",aes(y=df$MC_D))+
  geom_point(aes(y=df$MC_D))+
  ggtitle("D")+
  xlab("Tons of Carbon Emitted")+
  ylab("Marginal Cost\nof Abatement ($)")+
  #ylim(-15,150)+
  theme_classic()

plot_grid(a,b,c,d)
```

- Sector A: Linear

- Sector B: Logistic or linear

- Sector C: Exponential

- Sector D: Linear

###Inidividual models for each sector

####Sector A.
```{r sector_A}
#a
#Linear model
A_lm <- lm(MC_A ~ Abatement, data=df)
summary(A_lm)

#Assessing the model
#plot(A_lm)
#AIC(A_lm)
```

Using Sector A's linear model equation to make predicitons
```{r a_predictions}
#Vector to make predictions
A_vector <- seq(0,180,length.out=181)
summary(A_lm)

#Predictions
A_preds <- predict(A_lm, list(Abatement = A_vector),se.fit=TRUE)

#Data frame
A_df <- data.frame(A_vector, A_preds)
colnames(A_df) <- c("Abatement","MC_A","SE","DF","residuals")
A_df$MB_A <- rev(A_df$MC_A)

#Plot
a2 <- ggplot(data=A_df, aes(x=Abatement, y=MC_A))+
  geom_line()+
  geom_point(data=df, aes(x=Abatement, y=MC_A))+
  geom_line(data=A_df, aes(y=MB_A))
a2
```

####Sector B
Integrated logistic Growth Equation

$$Cost(Abatement) = \frac{Max~Value}{(1+B*e^{rt})}$$

```{r sector_B_model}
#b

#Initial estimates for values in the equation based on plot
#-Max = 40
#-C0 = 12
#-B = (40-12)/12 ~ 2.33333

#Logistic model using NLS
#B_nls <- nls(MC_B ~ maxValue/(1 + B*exp(-r*Abatement)),
#                data = df,
#                start = list(maxValue = 40, B = 2.33333, r = 0.006224),
#                trace = TRUE)
#summary(B_nls)

#Coefficient values from the model
#maxValue <- coef(B_abatement_fit)[1]
#B <- coef(B_abatement_fit)[2]
#r <- coef(B_abatement_fit)[3]

#Linear model
B_lm <- lm(MC_B ~ Abatement, data=df)
summary(B_lm)

#Comparing the models
#plot(B_lm)
#plot(B_nls)

AIC(B_lm)
#AIC(B_nls)

#Predictions and plot using nls
B_vector <- seq(0, 220, length = 221)
#B_preds_nls <- predict(B_nls, list(Abatement = B_vector), se.fit=TRUE,df=FALSE)

#B_df_nls <- data.frame(B_vector, B_preds_nls)
#colnames(B_df_nls) <- c("Abatement","MC_B")
#B_df_nls$MB_B <- rev(B_df_nls$MC_B)

#ggplot(data=df, aes(x=Abatement, y=MC_B))+
#  geom_point(color="blue", size = 3)+
#  geom_line(data=B_df_nls, aes(x=Abatement, y=MC_B))+
#  geom_line(data=B_df_nls, aes(x=Abatement, y=MB_B))

#Predictions and plot using lm
B_preds_lm <- predict(B_lm, list(Abatement = B_vector), se.fit=TRUE, df=FALSE)

B_df_lm <- data.frame(B_vector, B_preds_lm$fit,B_preds_lm$se.fit)
colnames(B_df_lm) <- c("Abatement","MC_B","SE")
B_df_lm$MB_B <- rev(B_df_lm$MC_B)

b2 <- ggplot(data=df, aes(x=Abatement, y=MC_B))+
  geom_point(color="blue", size = 3)+
  geom_line(data=B_df_lm, aes(x=Abatement, y=MC_B))+
  geom_line(data=B_df_lm, aes(x=Abatement, y=MB_B))
b2
```

####Sector C. 
$$Cost(x) = Y + a*x + b*x^2$$
Y = 10
a = 1.17
b = 5
```{r sector_c}
#Exponential model
#C_nls <- nls(MC_C ~ (0 + a*(Abatement)^2),
#                data = df,
#                start = list(a=5),
#                trace = TRUE)
#summary(C_nls)

#linear model

C_lm <- lm(MC_C~Abatement, data=df)
summary(C_lm)

#Comparing models
#plot(lm_C)
#plot(C_nls)

#Based on AIC, exponential model is a better fit for the data. 
AIC(C_lm)
AIC(C_nls)
```

```{r predictions_and_plot}
C_vector <- seq(0, 220, length = 221)
C_preds <- predict(C_lm, list(Abatement = C_vector), se.fit=TRUE)

C_df_lm <- data.frame(C_vector, C_preds$fit)
colnames(C_df_lm) <- c("Abatement","MC_C")
C_df_lm$MB_C <- rev(C_df_lm$MC_C)

c2 <- ggplot(data=df, aes(x=Abatement, y=MC_C))+
  geom_point(color="blue", size = 3)+
  geom_line(data=C_df_lm, aes(x=Abatement, y=MB_C))+
  geom_line(data=C_df_lm, aes(x=Abatement, y=MC_C))
c2
```

####Sector D
```{r linear model}
#d

D_lm <- lm(MC_D ~ Abatement, data=df)
#summary(D_lm)
#plot(D_lm)

D_vector <- seq(0,300,length.out = 301)
D_preds <- predict(D_lm, list(Abatement=D_vector),se.fit = TRUE)

D_df <- data.frame(D_vector, D_preds)
colnames(D_df) <- c("Abatement","MC_D")
D_df$MB_D <- rev(D_df$MC_D)

d2 <- ggplot(data=df, aes(x=Abatement, y=MC_D))+
  geom_point(color="blue", size = 3)+
  geom_line(data=D_df, aes(x=Abatement, y=MB_D))+
  geom_line(data=D_df, aes(x=Abatement, y=MC_D))

plot_grid(a2,b2,c2,d2)
```

```{r}
max <- 180+200+220
Q_bar <- max/2
```

```{r a_demand}
a_demand <- lm(MB_A ~ Abatement, data = A_df)
summary(a_demand)
a_demand$coefficients
```

```{r b_demand}
b_demand <- lm(MB_B ~ Abatement, data=B_df_lm)
summary(b_demand)
```

```{r c_demand}
C_demand <- lm(MB_C ~ Abatement, data=C_df_lm)
summary(C_demand)
```

```{r demand}
#A Demand curve
#P(Q) = 95.19-.5768(Q)
#Q(P) = (95.19-P)/.5768

#B Demand Curve
#P(Q) = 49.07-.1987*Q
#Q(P) = (49.07-P)/.1987

#C Demand Curve
#P(Q) = 160-.1987*Q
#Q(P) = (160.07-P)/.1987

A_D_intercept <- a_demand$coefficients[1]
A_D_slope <- a_demand$coefficients[2]

B_D_intercept <- b_demand$coefficients[1]
B_D_slope <- b_demand$coefficients[2]

C_D_intercept <- C_demand$coefficients[1]
C_D_slope <- C_demand$coefficients[2]

Ag_Dfun_P <- function(P){
  A_D <- ifelse(((A_D_intercept-P)/(-A_D_slope))<0,0,(A_D_intercept-P)/(-A_D_slope))
  B_D <- ifelse(((B_D_intercept-P)/(-B_D_slope))<0,0,(B_D_intercept-P)/(-B_D_slope))
  C_D <- ifelse(((C_D_intercept-P)/(-C_D_slope))<0,0,(C_D_intercept-P)/(-C_D_slope))
  Ag_Q <- A_D + B_D + C_D
  return(Ag_Q)
}

A_DFun_P <- function(P){
  A_D <- ifelse(((A_D_intercept-P)/(-A_D_slope))<0,0,(A_D_intercept-P)/(-A_D_slope))
  return(A_D)
}

B_DFun_P <- function(P){
  B_D <- ifelse(((B_D_intercept-P)/(-B_D_slope))<0,0,(B_D_intercept-P)/(-B_D_slope))
  return(B_D)
}

C_DFun_P <- function(P){
  C_D <- ifelse(((C_D_intercept-P)/(-C_D_slope))<0,0,(C_D_intercept-P)/(-C_D_slope))
  return(C_D)
}

Price <- seq(0,160,length.out=161)
ag_Demand <- Ag_Dfun_Q(Price)
demand <- data.frame(Price,ag_Demand,A_demandFun_P(Price),B_demandFun_P(Price),C_demandFun_Q(Price))
colnames(demand) <- c("Price","Aggregate","SectorA","SectorB","SectorC")

ag_plot <- ggplot(demand, aes(x=Aggregate,y=Price))+
  geom_line()+
  geom_line(aes(x=SectorA),color="goldenrod3")+
  geom_line(aes(x=SectorB),color="darkblue")+
  geom_line(aes(x=SectorC),color="red")+
  scale_x_continuous(expand = c(0, 0))+
  scale_y_continuous(expand = c(0, 0))
ag_plot
```

```{r}
kink1_Q <- C_demandFun_P(A_D_intercept)
kink2_Q <- C_demandFun_P(B_D_intercept)+A_demandFun_P(B_D_intercept)

seg1_slope <- (C_D_intercept-A_D_intercept)/(0-kink1_Q)
seg1_intercept <- C_D_intercept

seg2_slope <- (A_D_intercept-B_D_intercept)/(kink1_Q-kink2_Q)
seg2_intercept <- A_D_intercept - seg2_slope*kink1_Q

seg3_slope <- (B_D_intercept - 0)/(kink2_Q - 617.027573)
seg3_intercept <- B_D_intercept - seg3_slope*kink2_Q


seg1_fun_P <- function(Q){
  P <- seg1_intercept + seg1_slope*Q
  return(P)
}

seg2_fun_P <- function(Q){
 P <- seg2_intercept + seg2_slope*Q
  return(P)
}
 
seg3_fun_P <- function(Q){
P <- seg3_intercept + seg3_slope*Q
  return(P)
}
```

```{r 3a}
#demand functions WRT Q
A_DFun_Q <- function(Q){
  A_D_Q <- A_D_intercept + A_D_slope*Q
  return(A_D_Q)
}

B_DFun_Q <- function(Q){
  B_D_Q <- B_D_intercept + B_D_slope*Q
  return(B_D_Q)
}

C_DFun_Q <- function(Q){
  C_D_Q <- C_D_intercept + C_D_slope*Q
  return(C_D_Q)
  }

#Cost to each sector of not being able emit the last 100 units of pollution 
A_xint <- A_demandFun_P(0)
sectorA_cost_CC <- integrate(A_DFun_Q,lower=(A_xint-100),upper=(A_xint))
sectorA_cost_CC

B_xint <- B_demandFun_P(0)
sectorB_cost_CC <- integrate(B_DFun_Q,lower=(B_xint-100),upper=(B_xint))
sectorB_cost_CC

C_xint <- C_demandFun_P(0)
sectorC_cost_CC <- integrate(C_DFun_Q,lower=(C_xint-100),upper=(C_xint))
sectorC_cost_CC

#Total cost of carbon cap without trade
total_cost_CC2 <- sectorA_cost_CC$value  + sectorB_cost_CC$value + sectorC_cost_CC$value
total_cost_CC

#No tax, so no tax revenue
```


```{r 3b}
ag_plot
#Carbon tax should be equal to the difference between the current cost of pollution and the cost of pollution that would bring emissions down to 300
carbon_tax <- seg3_fun_P(300)

sectorA_taxQ <- A_DFun_P(carbon_tax)
sectorB_taxQ <- B_DFun_P(carbon_tax)
sectorC_taxQ <- C_DFun_P(carbon_tax)

sectorA_tax_cost <- integrate(A_DFun_Q,lower=(A_xint-sectorA_taxQ),upper=(A_xint))
SectorB_tax_cost <- integrate(B_DFun_Q,lower=(B_xint - sectorB_taxQ),upper=(B_xint))
SectorC_tax_cost <- integrate(C_DFun_Q,lower=(C_xint - sectorC_taxQ),upper=(C_xint))

SectorC_tax_cost$value

#total_cost_Tax <- integrate(seg3_fun_P,lower=300,upper=615)
#total_cost_Tax$value

tax_revenue <- 300*carbon_tax
tax_revenue
```

