---
title: "3_EconHW4"
author: "Claire Powers"
date: "May 31, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r packages_data, include=FALSE}
library(tidyverse)
library(cowplot)
library(nlstools)
library(stats)
library(reshape2)
library(stats)

df <- read.csv("HW4Data.csv")
```

###Initial plots and exploring the data

- Red lines are linear models, blue lines are "loess" which basically just follows the data points
```{r Initial_plots, echo=FALSE}
a <- ggplot(df, aes(x=df$Abatement))+
  geom_smooth(method="loess",aes(y=df$MC_A))+
  geom_smooth(method="lm",se=F,color="red",aes(y=df$MC_A))+
  geom_point(aes(y=df$MC_A))+
  #ylim(-15,150)+
  ggtitle("A")+
  xlab("Tons of Carbon Emitted")+
  ylab("Marginal Cost\nof Abatement ($)")+
  theme_classic()

b <- ggplot(df, aes(x=df$Abatement))+
  geom_smooth(method="loess",aes(y=df$MC_B))+
  geom_smooth(method="lm",se=F,color="red",aes(y=df$MC_B))+
  geom_point(aes(y=df$MC_B))+
  #ylim(-15,150)+
  ggtitle("B")+
  xlab("Tons of Carbon Emitted")+
  ylab("Marginal Cost\nof Abatement ($)")+
  theme_classic()

c <- ggplot(df, aes(x=df$Abatement))+
  geom_smooth(method="loess",aes(y=df$MC_C))+
  geom_smooth(method="lm",se=F,color="red",aes(y=df$MC_C))+
  geom_point(aes(y=df$MC_C))+
  ggtitle("C")+
  xlab("Tons of Carbon Emitted")+
  ylab("Marginal Cost\nof Abatement ($)")+
  #ylim(-15,150)+
  theme_classic()

d <- ggplot(df, aes(x=df$Abatement))+
  geom_smooth(method="loess",se=F,aes(y=df$MC_D))+
  geom_smooth(method="lm",se=F,color="red",aes(y=df$MC_D))+
  geom_point(aes(y=df$MC_D))+
  ggtitle("D")+
  xlab("Tons of Carbon Emitted")+
  ylab("Marginal Cost\nof Abatement ($)")+
  #ylim(-15,150)+
  theme_classic()

plot_grid(a,b,c,d)
```

- Sector A: Linear

- Sector B: Logistic or linear

- Sector C: Exponential

- Sector D: Linear

###Inidividual models for each sector

####Sector A.
```{r sector_A}
#a
#Linear model
A_lm <- lm(MC_A ~ Abatement, data=df)
summary(A_lm)

#Assessing the model
#plot(A_lm)
AIC(A_lm)
```

Using Sector A's linear model equation to make predicitons
```{r a_predictions}
#Vector to make predictions
A_vector <- seq(0,180,length.out=181)

#Predictions
A_preds <- predict(A_lm, list(Abatement = A_vector),se.fit=TRUE)

#Data frame
A_df <- data.frame(A_vector, A_preds)
colnames(A_df) <- c("Abatement","MC_A","SE","DF","residuals")
A_df$MB_A <- rev(A_df$MC_A)

#Plot
a2 <- ggplot(data=A_df, aes(x=Abatement, y=MC_A))+
  geom_line()+
  geom_point(data=df, aes(x=Abatement, y=MC_A))+
  geom_line(data=A_df, aes(y=MB_A))
a2
```

####Sector B
Integrated logistic Growth Equation

$$Cost(Abatement) = \frac{Max~Value}{(1+B*e^{rt})}$$

```{r sector_B_model}
#b

#Initial estimates for values in the equation based on plot
#-Max = 40
#-C0 = 12
#-B = (40-12)/12 ~ 2.33333

#Logistic model using NLS
B_nls <- nls(MC_B ~ maxValue/(1 + B*exp(-r*Abatement)),
                data = df,
                start = list(maxValue = 40, B = 2.33333, r = 0.006224),
                trace = TRUE)
#summary(B_nls)

#Coefficient values from the model
#maxValue <- coef(B_abatement_fit)[1]
#B <- coef(B_abatement_fit)[2]
#r <- coef(B_abatement_fit)[3]

#Linear model
B_lm <- lm(MC_B ~ Abatement, data=df)
summary(B_lm)

#Comparing the models
#plot(B_lm)
#plot(B_nls)

AIC(B_lm)
AIC(B_nls)

#Predictions and plot using nls
B_vector <- seq(0, 200, length = 201)
B_preds_nls <- predict(B_nls, list(Abatement = B_vector), se.fit=TRUE,df=FALSE)

B_df_nls <- data.frame(B_vector, B_preds_nls)
colnames(B_df_nls) <- c("Abatement","MC_B")
B_df_nls$MB_B <- rev(B_df_nls$MC_B)

ggplot(data=df, aes(x=Abatement, y=MC_B))+
  geom_point(color="blue", size = 3)+
  geom_line(data=B_df_nls, aes(x=Abatement, y=MC_B))+
  geom_line(data=B_df_nls, aes(x=Abatement, y=MB_B))

#Predictions and plot using lm
B_preds_lm <- predict(B_lm, list(Abatement = B_vector), se.fit=TRUE, df=FALSE)

B_df_lm <- data.frame(B_vector, B_preds_lm$fit,B_preds_lm$se.fit)
colnames(B_df_lm) <- c("Abatement","MC_B","SE")
B_df_lm$MB_B <- rev(B_df_lm$MC_B)

b2 <- ggplot(data=df, aes(x=Abatement, y=MC_B))+
  geom_point(color="blue", size = 3)+
  geom_line(data=B_df_lm, aes(x=Abatement, y=MC_B))+
  geom_line(data=B_df_lm, aes(x=Abatement, y=MB_B))
b2
```

####Sector C. 
$$Cost(x) = Y + a*x + b*x^2$$
Y = 10
a = 1.17
b = 5
```{r sector_c}
#Exponential model
C_nls <- nls(MC_C ~ (Y + a*Abatement + b*(Abatement^2)),
                data = df,
                start = list(Y = 10, a = 1.17, b = 5),
                trace = TRUE)
summary(C_nls)

#Coefficients from the model
Y <- coef(C_nls)[1]
Y
a <- coef(C_nls)[2]
a
b <- coef(C_nls)[3]
b

#linear model
C_lm <- lm(MC_C~Abatement, data=df)
summary(C_lm)

#Comparing models
#plot(lm_C)
#plot(C_nls)

#Based on AIC, exponential model is a better fit for the data. 
AIC(C_lm)
AIC(C_nls)
```

```{r predictions_and_plot}
C_vector <- seq(0, 220, length = 221)
C_preds <- predict(C_nls, list(Abatement = C_vector), se.fit=TRUE)

C_df_nls <- data.frame(C_vector, C_preds)
colnames(C_df_nls) <- c("Abatement","MC_C")
C_df_nls$MB_C <- rev(C_df_nls$MC_C)

c2 <- ggplot(data=df, aes(x=Abatement, y=MC_C))+
  geom_point(color="blue", size = 3)+
  geom_line(data=C_df_nls, aes(x=Abatement, y=MB_C))+
  geom_line(data=C_df_nls, aes(x=Abatement, y=MC_C))
```

####Sector D
```{r linear model}
#d

D_lm <- lm(MC_D ~ Abatement, data=df)
#summary(D_lm)
#plot(D_lm)

D_vector <- seq(0,300,length.out = 301)
D_preds <- predict(D_lm, list(Abatement=D_vector),se.fit = TRUE)

D_df <- data.frame(D_vector, D_preds)
colnames(D_df) <- c("Abatement","MC_D")
D_df$MB_D <- rev(D_df$MC_D)

d2 <- ggplot(data=df, aes(x=Abatement, y=MC_D))+
  geom_point(color="blue", size = 3)+
  geom_line(data=D_df, aes(x=Abatement, y=MB_D))+
  geom_line(data=D_df, aes(x=Abatement, y=MC_D))

plot_grid(a2,b2,c2,d2)
```

```{r}
max <- 180+200+220
Q_bar <- max/2


```

```{r a_demand}

a_demand <- lm(MB_A ~ Abatement, data = A_df)
summary(a_demand)
```

```{r b_demand}

b_demand <- lm(MB_B ~ Abatement, data=B_df_lm)
summary(b_demand)
```

```{r}
C_demand <- nls(MB_C ~ (Y * exp^(-Abatement)),
                data = df,
                start = list(Y = ),
                trace = TRUE)
summary(C_demand)
```

